Predicting the 2024 US Presidential Election: A Polling-Based Forecast

### 2024-10-26 paper/paper.qmd
Add files via upload

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-frequency-bar
#| fig-cap: Frequency of each pollster
#| echo: false
ggplot(analysis_data, aes(y = reorder(pollster, table(pollster)[pollster]))) +  
  geom_bar(aes(fill = after_stat(count)), color = "black") +                          
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.1, size = 2) +  
  scale_fill_gradient(low = "lightblue", high = "blue") +
  labs(x = "Count", y = "Pollster") +       
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8)) 
```
```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-avg-pollscore
#| fig-cap: Average Pollscore by Pollster and End Date
#| echo: false
# 假设要查看 pollster 和 end_date 组合上的 pollscore 平均值
library(dplyr)

# 计算每个 pollster 和 end_date 的平均 pollscore
heatmap_data <- analysis_data %>%
  group_by(pollster, end_date) %>%
  summarise(mean_pollscore = mean(pollscore, na.rm = TRUE), .groups = "drop")

# 绘制热图
ggplot(heatmap_data, aes(x = end_date, y = pollster, fill = mean_pollscore)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(x = "End Date", y = "Pollster", fill = "Avg Pollscore") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8))

>>>>

```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-frequency-bar
#| fig-cap: Frequency of each pollster
#| echo: false
ggplot(analysis_data, aes(y = reorder(pollster, table(pollster)[pollster]))) +  
  geom_bar(aes(fill = after_stat(count)), color = "black") +                          
  geom_text(stat = "count", aes(label = after_stat(count)), hjust = -0.1, size = 2) +  
  scale_fill_gradient(low = "lightblue", high = "blue") +
  labs(x = "Count", y = "Pollster") +       
  theme_minimal() +
  theme(axis.text.x = element_text(size = 8)) 
```
```{r, fig.pos= 'H', fig.width=8, fig.height=4}
#| label: fig-avg-pollscore
#| fig-cap: Average Pollscore by Pollster and End Date
#| echo: false
library(dplyr)

heatmap_data <- analysis_data %>%
  group_by(pollster, end_date) %>%
  summarise(mean_pollscore = mean(pollscore, na.rm = TRUE), .groups = "drop")

ggplot(heatmap_data, aes(x = end_date, y = pollster, fill = mean_pollscore)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(x = "End Date", y = "Pollster", fill = "Avg Pollscore") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(size = 8))
